Last glacial cycle glacier erosion potential in the Alps

### 2021-06-14 articles/erosion/response-editor.tex

% Copyright (c) 2021, Julien Seguinot (juseg.github.io), Ian Delaney
% Creative Commons Attribution-ShareAlike 4.0 International License
% (CC BY-SA 4.0, http://creativecommons.org/licenses/by-sa/4.0/) -->

\input{response-header}

\title{Authors' response to the Editor}
\author{J. Seguinot, on behalf of all authors.}
%\date{}

\begin{document}
\thispagestyle{empty}
\maketitle
\bigskip

    Dear Andreas Lang,

    We apologize for the delays during the peer review of our manuscript. We
    believe that we have addressed all points raised by the reviews and hereby
    submit our revised version to \emph{Earth Surface Dynamics}.

    Please find hereafter a short summary and a marked-up file listing changes
    made to the manuscript since its first publication as a preprint. If
    possible, we ask you to please refer to our public responses for more
    detailed point-by-point lists of changes.

    \begin{itemize}

        \item \textbf{Sect. 2 (Methods):}
        We made explicit the input topography and temperature records used in
        the parent study (Seguinot et~al., 2018), clarified simplifications
        made when computing erosion rates from basal velocities, and,
        accordingly, refer to the resulting quantities as ``erosion potential''
        in the entire manuscript.

        \item \textbf{Sect. 4 (Discussion):}
        We added sentences and whole paragraphs to discuss the systematic
        eastwards bias of ice cover (and thus erosion potential), the magnitude
        of our computed erosion potential versus expectable glacial cycle
        erosion, the uncertainties on basal sliding, and model limitations in
        high mountains due to resolution and approximated physics.

        \item \textbf{Figures:}
        We added scale bars on all map figures, and hatched regions on Figs.~1,
        2, 4 and~6 to indicate low confidence in our results for small
        glaciers. We added the field-based LGM outline on Fig.~1 (ex-Fig.~2),
        used different line styles to distinguish glacier advance and retreat
        on Fig.~2 (ex-Fig.~3), added glacier-advance (36 ka) and ice-free
        (0\,ka) erosion maps of the Rhine Glacier on Fig.~3 (ex-Fig.~4),
        plotted glaciated hypsometry and cumulative erosion per elevation band
        on Fig.~4 (ex-Fig.~5), made style changes to improve readability of
        Figs.~6 and 7 (ex-Figs.~7 and~8), moved Fig.~8 (ex-Fig.~1) into the
        discussion and replaced one of the photos.

        \item \textbf{Text improvements}
        were made throughout the text and figure captions following suggestions
        from the reviewers.

    \end{itemize}

    We thank you again very much for your editorial work on our manuscript.

\end{document}

### 2021-06-14 articles/erosion/response-editor.tex

\begin{document}
\thispagestyle{empty}
\maketitle
\bigskip

    Dear Andreas Lang,

    We apologize for the delays during the peer review of our manuscript. We
    believe that we have addressed all points raised by the reviews and hereby
    submit our revised version to \emph{Earth Surface Dynamics}.

    Please find hereafter a short summary (and attached, a marked-up file)
    listing changes
    made to the manuscript since its first publication as a preprint. If
    possible, we ask you to please refer to our public responses for more
    detailed point-by-point lists of changes.

@@

        \item \textbf{Sect. 2 (Methods):}
        We made explicit the input topography and temperature records used in
        the parent study (Seguinot et~al., 2018), clarified simplifications
        made when computing erosion rates from basal velocities, and,
        accordingly, refer to the resulting quantities as ``erosion potential''
        in the entire manuscript.

        \item \textbf{Sect. 4 (Discussion):}
        We added sentences and whole paragraphs to discuss the systematic
        eastwards bias of ice cover (and thus erosion potential), the magnitude
        of our computed erosion potential versus expectable glacial cycle
        erosion, the uncertainties on basal sliding, and model limitations in
        high mountains due to resolution and approximated physics.

        \item \textbf{Figures:}
        We added scale bars on all map figures, and hatched regions on Figs.~1,
        2, 4 and~6 to indicate low confidence in our results for small
        glaciers. We added the field-based LGM outline on Fig.~1 (ex-Fig.~2),
        used different line styles to distinguish glacier advance and retreat
        on Fig.~2 (ex-Fig.~3), added glacier-advance (36 ka) and ice-free
        (0\,ka) erosion maps of the Rhine Glacier on Fig.~3 (ex-Fig.~4),
        plotted glaciated hypsometry and cumulative erosion per elevation band
        on Fig.~4 (ex-Fig.~5), made style changes to improve readability of
        Figs.~6 and 7 (ex-Figs.~7 and~8), moved Fig.~8 (ex-Fig.~1) into the
        discussion and replaced one of the photos.

        \item \textbf{Supplementary figures:}
        This was not mentioned in our responses. Following the reviews, and
        if this does not result in additional page charges, we would like to
        amend a supplementary document containing copies of Figs.~1--5, and
        their equivalent as plotted with alternative erosion laws (more
        briefly presented in the manuscript Fig.~6). Comments from both
        reviewers highlight the difficulty of labelling any of the tested
        erosion laws more ``realistic'' (this wording was removed), and the
        supplementary figures may prove useful alongside future developments of
        empirical glacier erosion laws.

### 2021-07-09 articles/erosion/alps-erosion.tex
Fix agg data date, update erosion doi, tag 3.1.

    The ice-sheet model set-up was presented in an earlier publication
    \citep{Seguinot.etal.2018} and is briefly summarized here. The simulations
    were conducted using the Parallel Ice Sheet Model (PISM, development
    version~e9d2d1f), an open-source, finite-difference, shallow-ice and
    shallow-shelf model \citep{PISM-authors.2017}. Our setup includes
    temperature and water-content dependent creep, pseudo-plastic basal
    sliding, bedrock isostatic deformation under the ice
    load, and a~positive degree-day (PDD) surface mass balance model. The model
    is initialized with assumed present-day ice thickness and 1-km resolution
    bedrock topography from SRTM \citep{Jarvis.etal.2008},
    ice and bedrock temperature at 120\,ka (thousand years before the present),
    and is run to the present. The ice-sheet model physical parameters are listed
    in the earlier open-access publication \citep{Seguinot.etal.2018}, and the
    complete list of PISM
    parameters is stored in long-term archived model output metadata for the
    present study \citep{Seguinot.2021}, and for the earlier publication
    \citep{Seguinot.2020, Seguinot.2020a}.

@@

\codedataavailability{%
    PISM is available as open-source software (http://pism-docs.org).
    Time and domain-aggregated erosion variables such as used in the figures is
    available for the four presented erosion power-laws
    (\doi{10.5281/zenodo.4495419}). Other model output variables were
    previously made available (\doi{10.5281/zenodo.3604174},
    \doi{10.5281/zenodo.3604142}).}

>>>>

    The ice-sheet model set-up was presented in an earlier publication
    \citep{Seguinot.etal.2018} and is briefly summarized here. The simulations
    were conducted using the Parallel Ice Sheet Model (PISM, development
    version~e9d2d1f), an open-source, finite-difference, shallow-ice and
    shallow-shelf model \citep{PISM-authors.2017}. Our setup includes
    temperature and water-content dependent creep, pseudo-plastic basal
    sliding, bedrock isostatic deformation under the ice
    load, and a~positive degree-day (PDD) surface mass balance model. The model
    is initialized with assumed present-day ice thickness and 1-km resolution
    bedrock topography from SRTM \citep{Jarvis.etal.2008},
    ice and bedrock temperature at 120\,ka (thousand years before the present),
    and is run to the present. The ice-sheet model physical parameters are listed
    in the earlier open-access publication \citep{Seguinot.etal.2018}, and the
    complete list of PISM
    parameters is stored in long-term archived model output metadata for the
    present study \citep{Seguinot.2021}, and for the earlier publication
    \citep{Seguinot.2019, Seguinot.2020}.

@@

\codedataavailability{%
    PISM is available as open-source software (http://pism-docs.org).
    Time and domain-aggregated erosion variables such as used in the figures is
    available for the four presented erosion power-laws
    (\doi{10.5281/zenodo.5084579}). Other model output variables were
    previously made available (\doi{10.5281/zenodo.3604174},
    \doi{10.5281/zenodo.3604142}).}
